### 2019-05-07 2-Chapters/5-Chapter/chapter5.tex
Done... So tired.

% ----------------------------------------------------------------------------
% ----------------------------------------------------------------------------
\section{Literature review of many extensions of our models}
\label{sec:5:literatureReviewOtherModels}
% ----------------------------------------------------------------------------

@@

\TODOL{
    Pour les extension présentées ici, je veux suivre la même organisation :

    1. j'explique l'extension, et en quoi c'est difficile (= en quoi notre approche échoue si on fait rien de plus),

    2. j'explique les travaux existants, et les résultats qu'ils obtiennent e.g. en terme de bornes de regret

    3. si j'ai déjà le code pour, je peux montrer UNE simulation
}

@@

@@

In all the models of IoT networks considered in this thesis, we assume that \emph{the different IoT devices cannot communicate with each other}, and can only communicate with a unique gateway.
Of course, this hypothesis can be removed, and in practice in some families of wireless networks, communication between devices are possible.
Note that this extension is not considering a graph of distributed agents all playing cooperatively to solve a unique bandit game, like it is studied in the ``graph bandit'' problem.
What we are interested here is an extension of our model where players can send some bits to one or all the other players, at every time steps or some time steps.

@@

In the multi-player model presented in this chapter, we assume that the arm distributions are the same for all the players.
For cognitive radio applications, where arms model channels and players are radio devices, it can be unrealistic to consider that two players, maybe located at different distances from the gateway or equipped with different hardwares, encounter the same mean quality when accessing the same channel.
%
Motivated by this weakness, some researchers studied an interesting extension of our model of interest, considering multi-player MAB models with different arms distributions among players.
%
Starting in 2012 by \cite{Kalathil12} where arms are Markov chain, this model was studied more actively recently, \cite{DarakHanawal18,Bistritz18,KaufmannAbbas19,Tibrewal2019}.

@@

We have implemented in SMPyBandits \cite{SMPyBandits} the following extensions: evaluating $M$ on the fly (Section~\ref{sub:5:unknownNumberOfPlayers}), piece-wise stationary multi-player bandits (Section~\ref{sub:5:towardsNonStationaryModels}).
We have not yet implemented the other extensions of our model in SMPyBandits, but we are interested to do it, and it is one of the major future work left on our library.
For more details, see the issue tickets at \href{https://github.com/SMPyBandits/SMPyBandits/issues/}{\texttt{GitHub.com/SMPyBandits/SMPyBandits/issues/X}}, for tickets number \href{https://github.com/SMPyBandits/SMPyBandits/issues/120}{120}, \href{https://github.com/SMPyBandits/SMPyBandits/issues/124}{124}, \href{https://github.com/SMPyBandits/SMPyBandits/issues/185}{185}.

>>>>

\newpage  % WARNING
% ----------------------------------------------------------------------------
% ----------------------------------------------------------------------------
\section{Literature review of many extensions of our models}
\label{sec:5:literatureReviewOtherModels}
% ----------------------------------------------------------------------------

@@

% \TODOL{
%     Pour les extension présentées ici, je veux suivre la même organisation :

%     1. j'explique l'extension, et en quoi c'est difficile (= en quoi notre approche échoue si on fait rien de plus),

%     2. j'explique les travaux existants, et les résultats qu'ils obtiennent e.g. en terme de bornes de regret

%     3. si j'ai déjà le code pour, je peux montrer UNE simulation
% }

@@

\TODOL{Expliquer pourquoi ce n'est pas très réaliste ? Le paragraphe ci dessous n'est pas très simple à comprendre, je peux faire mieux!}

@@

In all the models of IoT networks considered in this thesis, we assume that \emph{the different IoT devices cannot communicate with each other}, and can only communicate with a unique gateway.
Of course, this hypothesis can be removed, and in practice in some families of wireless networks, communication between devices are possible.
Note that this extension is not considering a graph of distributed agents all playing cooperatively to solve a unique bandit game, like it is studied in the ``graph bandit'' problem.
What we are interested here is an extension of the model where players can send some bits to one or all the other players, at every time steps or some time steps.

@@

In the multi-player model presented in this chapter, we assume that the arm distributions are the same for all the players.
For cognitive radio applications, where arms model channels and players are radio devices, it can be unrealistic to consider that two players, maybe located at different distances from the gateway or equipped with different hardwares, encounter the same mean quality when accessing the same channel.
%
Motivated by this weakness, some researchers studied an interesting extension of the model of interest, considering multi-player MAB models with different arms distributions among players.
%
Starting in 2012 by \cite{Kalathil12} where arms are Markov chain, this model was studied more actively recently, \cite{DarakHanawal18,Bistritz18,KaufmannAbbas19,Tibrewal2019}.

@@

We have implemented in SMPyBandits \cite{SMPyBandits} the following extensions: evaluating $M$ on the fly (Section~\ref{sub:5:unknownNumberOfPlayers}), piece-wise stationary multi-player bandits (Section~\ref{sub:5:towardsNonStationaryModels}).
We have not yet implemented the other extensions, but we are interested to do it, and it is one of the major future work left on our library.
For more details, see the issue tickets at \href{https://github.com/SMPyBandits/SMPyBandits/issues/}{\texttt{GitHub.com/SMPyBandits/SMPyBandits/issues/X}}, for tickets number \href{https://github.com/SMPyBandits/SMPyBandits/issues/120}{120}, \href{https://github.com/SMPyBandits/SMPyBandits/issues/124}{124}, \href{https://github.com/SMPyBandits/SMPyBandits/issues/185}{185}.
